Left-linear rules in adhesive categories

### 2024-02-10 icalp/fusione.tex
minor things

\documentclass[a4paper,UKenglish,cleveref,pdftex, thm-restate,numberwithinsect]{lipics}
\newif\ifreport
\reporttrue
%\reportfalse

% full or conference version
\newif\iffull
\fulltrue
\fullfalse

@@

\title{Left-linear rules in adhesive categories}
\author{Paolo Baldan} 
{Department of Mathematics, University of Padova, Italy}
{baldan@math.unipd.it}{}{}
\author{Davide Castelnovo}
{Department of Mathematics, University of Padova, Italy}
{davide.castelnovo@math.unipd.it}{}{}
\author{Andrea Corradini}
{Department of Computer Science, University of Pisa, Italy}
{andrea.corradini@unipi.it}{}{}

@@

\begin{example}\todo{Topos, ipergrafi e grafi}
\end{example}

\begin{example}
  \todo{grafi semplici}
\end{example}

\begin{example}
  \todo{GRAFI GERARCHICI}
\end{example}

\begin{example}
  \todo{term graph}
\end{example}

@@

\todo[inline]{P: se non impatta sul resto forse sarebbe forse piu' carino definire:\\
  - for each $G \in \X$, $G : G \Mapsto G$ is a derivation\\  
  - for each direct derivation $\dder{D}: G \Mapsto H$ and derivation $\der{E} : H \Mapsto F$ we have that $\dder{D}; \der{E} : G \Mapsto F$ is a derivation
}

@@

>>>>

\documentclass[a4paper,UKenglish,cleveref,pdftex, thm-restate,numberwithinsect,anonymous]{lipics}
\newif\ifreport
\reporttrue
%\reportfalse

% full includes some additional material
\newif\iffull
\fulltrue
\fullfalse

@@

\title{Left-linear rules in adhesive categories}

\author{Paolo Baldan} 
{Department of Mathematics, University of Padova, Italy}
{baldan@math.unipd.it}{}{}
\author{Davide Castelnovo}
{Department of Mathematics, University of Padova, Italy}
{davide.castelnovo@math.unipd.it}{}{}
\author{Andrea Corradini}
{Department of Computer Science, University of Pisa, Italy}
{andrea.corradini@unipi.it}{}{}

@@

\begin{example}
  \label{ex:adhesive}
  Every topos is adhesive~\cite{lack2006toposes}, thus in particular
  $\cat{Set}$ is adhesive. By the closure properties recalled before
  every presheaf $[\cat{X},\cat{Set}]$ is adhesive and in particular
  the category $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is
  adhesive where $E \rightrightarrows {V}$ is the two object category
  with two morphisms $s,t \colon{E} \to {V}$. In a similar way,
  various categories of hypergraphs can be shown to be adhesive, while
  the category $\cat{sGraphs}$ of simple graphs, i.e., graphs without
  parallel edges is quasi-adhesive, i.e.,
  $\reg{(\cat{sGraphs})}$-adhesive.\todo{Add hierarchical graphs and term graphs\cite{castelnovo2023thesis,CastelnovoGM22}).}
\end{example}

@@

% \todo[inline]{P: se non impatta sul resto forse sarebbe forse piu' carino definire:\\
%   - for each $G \in \X$, $G : G \Mapsto G$ is a derivation\\  
%   - for each direct derivation $\dder{D}: G \Mapsto H$ and derivation $\der{E} : H \Mapsto F$ we have that $\dder{D}; \der{E} : G \Mapsto F$ is a derivation
% }

@@

\begin{example}[E-graphs]
  Graphs with equivalences on nodes. Formally $V \to$
\end{example}
